Report

### 2023-04-25 manuscript.Rmd
prepare preprint

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1,2"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Formal Analysis
      - Funding acquisition
      - Methodology
      - Project administration
      - Software
      - Supervision
      - Writing – original draft
      - Writing – review & editing
  - name: "Eli-Boaz Clapper"
    affiliation: "2"
    role:
      - Formal Analysis
      - Writing – original draft
      - Writing – review & editing
  - name: "Rebecca Kuiper"
    affiliation: "2"
    role:
      - Conceptualization
      - Writing – review & editing
affiliation:
  - id            : "1"
    institution   : "Tilburg University, dept. Methodology & Statistics"
  - id            : "2"
    institution   : "Utrecht University, dept. Methodology & Statistics"

authornote: |
  This is a preprint paper, generated from Git Commit # `r substr(gert::git_commit_id(),1,7)`. This work was funded by a NWO Veni Grant (NWO Grant Number VI.Veni.191G.090), awarded to the lead author.

abstract: |
  The product Bayes factor (PBF) can synthesize evidence for an informative hypothesis across heterogeneous replication studies. It is particularly useful when the number of studies is relatively low and conventional assumptions about between-studies heterogeneity are likely violated. The present paper introduces a user-friendly implementation of the PBF in the bain R-package, and demonstrates its use in several tutorial examples. The method was validated in a simulation study that manipulated sample size, number of replication samples, and reliability. PBF had a higher overall accuracy when benchmarked against other evidence synthesis methods, including random-effects meta-analysis (RMA). This was primarily due to PBF’s greater sensitivity in detecting a true effect. However, PBF had relatively lower specificity. The PBF showed increasing sensitivity and specificity with increasing sample size. With an increasing number of samples, lower sensitivity was traded for greater specificity. Although PBF's overall performance was less susceptible to reliability than the other algorithms, this masked a trade-off between reliability and specificity. PBF thus appears to be a promising method for meta-analysis of heterogeneous conceptual replication studies. Nonetheless, users should be aware of its lower specificity, and the fact that it takes a Bayesian approach to inference and addresses a qualitatively different research question than other evidence synthesis methods.

keywords          : "bayes factor, evidence synthesis, bayesian, meta-analysis"
wordcount         : "5356"

@@

```{r setup, include = FALSE}
run_everything <- TRUE
library("papaja")
library(tidySEM)
library(kableExtra)
library(pwr)
library(bain)
r_refs("r-references.bib")
source("UI function/pbf.R")
out <- readRDS("out.RData")
resultaction = "markup"
```

@@

A key challenge in quantitative research synthesis is dealing with between-studies heterogeneity [@higginsReevaluationRandomeffectsMetaanalysis2009].
When studies examine the same research question in different laboratories, use idiosyncratic methods, and sample from distinct populations, these between-study differences can introduce heterogeneity in findings.
The most common quantitative research synthesis method is meta-analysis,
in which results of different studies are aggregated to estimate an aggregate effect size [@borensteinIntroductionMetaAnalysis2009].
In meta-analysis, heterogeneity can be accounted for in four ways [see @vanlissaSmallSampleMetaanalyses2020].
First, if studies are exact replications,
one may assume that no heterogeneity in the outcome exists and a fixed-effect meta-analysis can be conducted to estimate the common population effect. 
Second, when heterogeneity between studies can be assumed to be random,
random-effects meta-analysis can be used to estimate the mean of a distribution of population effects. 
Third, when there are a few systematic differences between studies, these can be accounted for using meta-regression.
Finally, when there are many potential variables that cause systematic differences and it is not known beforehand which are relevant, exploratory techniques like random forest meta-analysis and penalized meta-regression can be used to identify relevant moderators [@vanlissaSelectRelevantModerators2021].
However, accounting for moderators requires a relatively high number of observations per moderator,
which may not be available.
Each of these approaches thus makes different assumptions about the nature of heterogeneity [see "Models for meta-analysis" in @vanlissaSmallSampleMetaanalyses2020].

A crucial shortcoming of existing research synthesis methods is that the aforementioned assumptions
may not be tenable when meta-analyzing studies that investigate the same informative hypothesis,
but are otherwise very heterogeneous.
The situation may arise where each study is uniquely identified by a combination of linearly dependent moderators.
In this case, it is no longer possible to synthesize *effect sizes* while accounting for heterogeneity using statistical methods.
<!-- even machine learning based methods cannot identify relevant moderators. -->
It is still possible, however, to quantify the support these studies provide for the underlying informative hypothesis.
To this end, Bayesian evidence synthesis (BES) aggregates the evidence for a theoretical relationship across studies,
without imposing assumptions about heterogeneity [@kuiperCombiningStatisticalEvidence2013].
Although this assumption is not necessary,
for the sake of simplicity we assume that this theoretical relationship is evaluated via informative hypothesis $H_i$ in all studies.

@@

This paper introduces the first implementation of BES in user-friendly free open source software (FOSS).
A function `pbf()` was contributed to the `bain` R-package for Bayesian informative hypothesis evaluation, version `0.2.9`.
<!-- `r as.character(packageVersion("bain"))`. -->
This paper presents a simulation study to validate the method and benchmark it against alternative evidence synthesis methods,
and illustrates several use cases through reproducible examples.

@@

As a benchmark for comparison, we included several other algorithms that might feasibly be used by researchers who intend to examine whether a hypothesis is true across several independent samples.
The first was *vote counting*: counting the number of significant effects.
Although this method is still in use for aggregating conceptual replications,
it is considered bad practice.
Three disadvantages are that vote counting disregards sample size,
reduces statistical power,
and does not quantify the strength of the evidence [@hedgesVotecountingMethodsResearch1980].
Our vote counting algorithm summed the number of one-sided z-tests of a null hypothesis corresponding to the informative hypothesis,
so $H_0: \rho = .1$ and $H_a: \rho > .1$, which corresponds to $H_i$.
The decision criterion was that the hypothesis was supported in the majority of samples.
Thus, for example, if $H_0$ was rejected in three out of five samples, our vote counting algorithm would find overall support for $H_a$ (and, by extension, $H_i$).

The third algorithm was *random-effects meta-analysis* (RMA),
which is the current gold standard for evidence synthesis [@viechtbauerConductingMetaanalysesMetafor2010].
For this algorithm, the null-hypothesis was rejected if the lower bound of a 90% confidence interval for the overall effect size excluded $H_i$.
Note that this corresponds to a test at $\alpha = .05$,
because all effects in the simulation are directional.

The fourth algorithm was *individual participant data* (IPD) meta-analysis [@rileyMetaanalysisIndividualParticipant2010].
Like classic meta-analysis (RMA), IPD is a multilevel model, clustered by sample.
IPD uses the raw data, which makes it possible to estimate variance at the first level.
By contrast, RMA treats the first-level variance as known.
Note that the PBF can be estimated using either sufficient statistics (as in meta-analysis) or using raw data (as in IPD).
With this in mind, it is informative to benchmark it against both of these methods.
IPD was also evaluated using the lower bound of a 90% confidence interval for the overall effect size.
<!-- Rebecca: -->
<!-- zou je dit vooraf moeten zeggen? -->
<!-- Dan zeggen dat ILP dit ook kan en dan zeggen dus dat ook als vergelijking meenemen? -->
<!-- Ms zelfs in intro dit al noemoen, dan zeggen dat er twee meta-an equivalenten zijn, waarin je null hypo testing kan doen. En we dat gaan meenemen om te vergelijken. -->

@@

```{r tabeffect, echo = FALSE}
tab <- read.csv("effect_of_conditions.csv", stringsAsFactors = FALSE)
tab <- tab[, !grepl("(gpbf|tbf)", names(tab))]
tab <- tab[, grepl("^\\w+$", names(tab)) | (grepl("\\.{2}", names(tab)) & grepl("PBF", names(tab)))]
names(tab)[grepl("\\.{2}", names(tab))] <- paste0("vs ", gsub("(\\.|PBF|vs)", "", names(tab)[grepl("\\.{2}", names(tab))]))
knitr::kable(tab, digits = 2, caption = "Partial eta squared of the effect of each design factor on accuracy for each algorithm and for the difference between PBF and all other algorithms (e.g., vs RMA).")
```
We used ANOVAs to examine the effect of simulation conditions on overall accuracy.
The differences between algorithms were analyzed in analyses that included two-way interactions between design factors and algorithm.
As the sample size was very large,
significance tests were uninformative.
We thus focused on interpreting the effect size of the effects of design factors.
The performance of PBF was most impacted by sample size $n$, followed by the number of groups $k$, and reliability.
The differences in the effects of sample size and number of groups were relatively small between PBF and the two best practice algorithms, RMA and IPD -
but substantial between PBF and the suboptimal VC algorithm.
The reverse pattern occurred for reliability, however:
it showed a substantial difference in effect between PBF and the two best practice algorithms only.

@@

Figure \@ref(fig:figk) indicates that, for PBF at higher levels of $k$,
lower sensitivity was traded for greater specificity.
The other algorithms did not show this pattern, as their specificity was at a ceiling.
This difference in pattern of effects explains why number of samples had a moderate effect on the difference between algorithms (see Table \@ref(tab:tabeffect)).
Only VC showed decreasing sensitivity with an increasing number of groups;
this is because the probability of obtaining false negatives increases with the number of groups [as also noted by @hedgesVotecountingMethodsResearch1980].

@@

<!-- In the first use-case of `pbf()`, an `lm()` is ran for each sample. All `lm` objects are stored in a list which is passed to `pbf()`. -->
<!-- `pbf()` supports lists of all objects that `bain()` also supports. All supported types are specified in bain vignette *REF*. One exception is the use of named vectors, which will be covered later. -->
<!-- ```{r} -->
<!-- lm_sample1 <- lm(postnumb~site-1, sample1) -->
<!-- lm_sample2 <- lm(postnumb~site-1, sample2) -->
<!-- lm_sample3 <- lm(postnumb~site-1, sample3) -->

@@

<!-- In the first use-case of `pbf()`, an `lm()` is ran for each country.  -->
<!-- All `lm` objects are stored in a list which is passed to `pbf()`. -->
<!-- `pbf()` supports lists of all objects that `bain()` also supports.  -->
<!-- All supported types are specified in the `bain` vignette.  -->
<!-- One exception is the use of named vectors, which will be covered later. -->
<!-- ```{r} -->
<!-- fit_US <- lm(soc ~ grp + her, data = USa) -->
<!-- fit_DK <- lm(soc ~ grp + her, data = DKa) -->
<!-- fit_NL <- lm(soc ~ grp + her, data = NLa) -->

@@

A third use-case occurs when the raw data from different samples are not available.
This may happen, for example, when aggregating findings from the published literature (similar to meta-analysis).
In this case, one can use the default interface of `bain`, as explained in [@hoijtink2019tutorial].
This function requires four arguments: A named vector of parameter estimates, their asymptotic covariance matrix, the original sample size, and the number of within-group and between-group parameters.
Note that, when analyzing a single parameter per sample, the standard error is sufficient to construct the asymptotic covariance matrix.
Thus, this method can be applied to data that have been prepared for classic meta-analysis (effect sizes and their sampling variances).
Importantly, unlike meta-analysis, the present method is suitable for conceptual replications.
It does not require uniform effect size measures across studies.
The example below illustrates how to aggregate evidence for one hypotheses across three studies that each used different methods.
<!-- CJ: What I'd like to do here is show how to aggregate a t-test, a regression coefficient and a correlation coefficient -->

@@

The results suggest substantial evidence for the hypothesis that there is a positive association between family morality and political conservatism.
Although each study used a different method to assess this hypothesis,

@@

<!-- It is interesting that these estimates are not identical to the other examples... Is that because we do not have ALL information available in this use-case, or is something off in the script? -->
<!-- CJ: We should ask Herbert about this, but this example won't make it into this paper. If you want, you can send Herbert a reproducible example of the 'problem'!-->

@@

In conclusion, this study evaluated the performance of the product Bayes factor as a method for evidence synthesis,
and compared it against other commonly used evidence synthesis methods under different simulation conditions.
Compared to the other methods,
PBF had the highest overall accuracy.
This was primarily due to its greater sensitivity.
However, PBF had lower specificity than all other algorithms, suggesting a trade-off between sensitivity and specificity.
The other algorithms showed ceiling effects in specificity, limiting their sensitivity.
The performance of the PBF was most strongly affected by sample size,
We introduced a user-friendly implementation of the PBF in the `bain` R-package,
and demonstrated its use with various analysis techniques in R,
as well as with sufficient statistics that are already routinely coded for meta-analysis (i.e., effect sizes and their sampling variance).
This means that researchers can now use the PBF to aggregate evidence in situations where classic meta-analytic methods are less suitable.
For example, when one informative hypothesis has been evaluated in several replication studies,
but these replication studies are quite heterogeneous because they sample from different populations and use different methods or analysis techniques.
Especially when the number of replication studies is too small to adequately account for these sources of between-study heterogeneity,
the PBF may be a useful method to aggregate evidence for the common informative hypothesis.
Researchers should be aware that the PBF trades off increased sensitivity for decreased specificity,
and that it addresses a different research question than other research synthesis methods.
This highlights the importance of careful interpretation of the results,
and consideration of the research question when selecting an aggregation method.
In sum,
our results suggest that PBF is a useful evidence synthesis method,
which is now broadly accessible due to its inclusion in the `bain` R-package.

>>>>

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1"
    corresponding: yes
    address: "Professor Cobbenhagenlaan 125, 5037 DB Tilburg, The Netherlands"
    email: "c.j.vanlissa@tilburguniversity.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Formal Analysis
      - Funding acquisition
      - Methodology
      - Project administration
      - Software
      - Supervision
      - Writing – original draft
      - Writing – review & editing
  - name: "Eli-Boaz Clapper"
    affiliation: "2"
    role:
      - Formal Analysis
      - Writing – original draft
      - Writing – review & editing
  - name: "Rebecca Kuiper"
    affiliation: "2"
    role:
      - Conceptualization
      - Writing – review & editing
affiliation:
  - id            : "1"
    institution   : "Tilburg University, dept. Methodology & Statistics"
  - id            : "2"
    institution   : "Utrecht University, dept. Methodology & Statistics"

authornote: |
  This is a preprint paper, generated from Git Commit # `r substr(gert::git_commit_id(),1,8)`. This work was funded by a NWO Veni Grant (NWO Grant Number VI.Veni.191G.090), awarded to the lead author.

abstract: |
  The product Bayes factor (PBF) can synthesize evidence for an informative hypothesis across heterogeneous replication studies. It is particularly useful when the number of studies is relatively low and conventional assumptions about between-studies heterogeneity are likely violated. The present paper introduces a user-friendly implementation of the PBF in the `bain` R-package.
  The method was validated in a simulation study that manipulated sample size, number of replication samples, and reliability. Several tutorial examples demonstrate the use of the method in distinct use cases. Results of the simulation study show that PBF had a higher overall accuracy when benchmarked against other evidence synthesis methods, including random-effects meta-analysis (RMA). This was primarily due to PBF’s greater sensitivity in detecting a true effect. However, PBF had relatively lower specificity. The PBF showed increasing sensitivity and specificity with increasing sample size. With an increasing number of samples, lower sensitivity was traded for greater specificity. Although PBF's overall performance was less susceptible to reliability than the other algorithms, this masked a trade-off between reliability and specificity. PBF thus appears to be a promising method for meta-analysis of heterogeneous conceptual replication studies. Nonetheless, users should be aware of its lower specificity, and the fact that the Bayesian approach to inference addresses a qualitatively different research question than other evidence synthesis methods.

keywords          : "bayes factor, evidence synthesis, bayesian, meta-analysis"
wordcount         : "5039"

@@

```{r setup, include = FALSE}
run_everything <- TRUE
library("papaja")
library(tidySEM)
library(kableExtra)
library(pwr)
library(bain)
r_refs("r-references.bib")
source("UI function/pbf.R")
out <- readRDS("out.RData")
resultaction = "hide" # "markup"
```

@@

A key challenge in quantitative research synthesis is dealing with between-studies heterogeneity [@higginsReevaluationRandomeffectsMetaanalysis2009].
When studies examine the same research question in different laboratories, use idiosyncratic methods, and sample from distinct populations, these between-study differences can introduce heterogeneity in findings.
The most common quantitative research synthesis method is meta-analysis,
in which results of different studies are aggregated to estimate an aggregate effect size [@borensteinIntroductionMetaAnalysis2009].
In meta-analysis, heterogeneity can be accounted for in four ways [see @vanlissaSmallSampleMetaanalyses2020].
First, if studies are exact replications,
one may assume that no heterogeneity in the outcome exists and a fixed-effect meta-analysis can be conducted to estimate the common population effect. 
Second, when heterogeneity between studies can be assumed to be random,
random-effects meta-analysis can be used to estimate the mean of a distribution of population effects. 
Third, when there are a few systematic differences between studies, these can be accounted for using meta-regression.
Finally, when there are many potential variables that cause systematic differences and it is not known beforehand which are relevant, exploratory techniques like random forest meta-analysis and penalized meta-regression can be used to identify relevant moderators [@vanlissaSelectingRelevantModerators2023].
However, accounting for moderators requires a relatively high number of observations per moderator,
which may not be available.

Each of the aforementioned approaches makes different assumptions about the nature of heterogeneity [see "Models for meta-analysis" in @vanlissaSmallSampleMetaanalyses2020].
A crucial shortcoming of existing research synthesis methods is that these assumptions
may not be tenable when meta-analyzing studies that investigate the same informative hypothesis,
but are otherwise very heterogeneous.
The situation may arise where each study is uniquely identified by a combination of linearly dependent moderators.
In this case, it is no longer possible to synthesize *effect sizes* while accounting for heterogeneity using statistical methods.
<!-- even machine learning based methods cannot identify relevant moderators. -->
It is still possible, however, to quantify the support these studies provide for the underlying informative hypothesis.
To this end, Bayesian evidence synthesis (BES) aggregates the evidence for a theoretical relationship across studies,
without imposing assumptions about heterogeneity [@kuiperCombiningStatisticalEvidence2013].
Although this assumption is not necessary,
for the sake of simplicity we assume that this theoretical relationship is evaluated via informative hypothesis $H_i$ in all studies.

@@

This paper introduces the first implementation of BES in user-friendly free open source software.
A function `pbf()` was contributed to the `bain` R-package for Bayesian informative hypothesis evaluation, version `0.2.9`.
<!-- `r as.character(packageVersion("bain"))`. -->
This paper presents a simulation study to validate the method and benchmark it against alternative evidence synthesis methods.
It additionally illustrates several use cases through reproducible examples.

@@

As a benchmark for comparison, we included several other algorithms that might feasibly be used by researchers who intend to examine whether a hypothesis is true across several independent samples.
The first benchmark was *vote counting*: counting the number of significant effects.
Although this method is still in use for aggregating conceptual replications,
it is considered bad practice.
Three disadvantages are that vote counting disregards sample size,
reduces statistical power,
and does not quantify the strength of the evidence [@hedgesVotecountingMethodsResearch1980].
Our vote counting algorithm summed the number of one-sided z-tests of a null hypothesis corresponding to the informative hypothesis,
so $H_0: \rho = .1$ and $H_a: \rho > .1$, which corresponds to $H_i$.
The decision criterion was that the hypothesis was supported in the majority of samples.
Thus, for example, if $H_0$ was rejected in three out of five samples, our vote counting algorithm would find overall support for $H_a$ (and, by extension, $H_i$).

The second benchmarking algorithm was *random-effects meta-analysis* (RMA),
which is the current gold standard for evidence synthesis [@viechtbauerConductingMetaanalysesMetafor2010].
For this algorithm, the null-hypothesis was rejected if a 90% confidence interval excluded the hypothesized value under $H_i$.
Note that a 90% confidence interval corresponds to a test at $\alpha = .05$,
because all effects in the simulation are directional.

The third benchmarking algorithm was *individual participant data* (IPD) meta-analysis [@rileyMetaanalysisIndividualParticipant2010].
Like classic meta-analysis (RMA), IPD is a multilevel model, clustered by sample.
IPD uses the raw data, which makes it possible to estimate variance at the first level.
By contrast, RMA treats the first-level variance as known.
Note that the PBF can be estimated using either sufficient statistics (as in meta-analysis) or using raw data (as in IPD).
With this in mind, it is informative to benchmark it against both of these methods.
Just as for RMA, a 90% confidence interval was used for inference.
<!-- Rebecca: -->
<!-- zou je dit vooraf moeten zeggen? -->
<!-- Dan zeggen dat ILP dit ook kan en dan zeggen dus dat ook als vergelijking meenemen? -->
<!-- Ms zelfs in intro dit al noemoen, dan zeggen dat er twee meta-an equivalenten zijn, waarin je null hypo testing kan doen. En we dat gaan meenemen om te vergelijken. -->

@@

```{r tabeffect, echo = FALSE}
tab <- read.csv("effect_of_conditions.csv", stringsAsFactors = FALSE)
tab <- tab[, !grepl("(gpbf|tbf)", names(tab))]
tab <- tab[, grepl("^\\w+$", names(tab)) | (grepl("\\.{2}", names(tab)) & grepl("PBF", names(tab)))]
names(tab)[grepl("\\.{2}", names(tab))] <- paste0("vs ", gsub("(\\.|PBF|vs)", "", names(tab)[grepl("\\.{2}", names(tab))]))
knitr::kable(tab, digits = 2, caption = "Partial eta squared of the effect of each design factor on accuracy for each algorithm and for the difference between PBF and all other algorithms (e.g., vs RMA).")
```
We used ANOVAs to examine the effect of simulation conditions on overall accuracy.
The differences between algorithms were analyzed in analyses that included two-way interactions between design factors and algorithm.
As the sample size was very large,
significance tests were uninformative.
We thus focused on interpreting the effect sizes of the design factors.
The performance of PBF was most impacted by sample size $n$, followed by the number of groups $k$, and reliability.
The differences in the effects of sample size and number of groups were relatively small between PBF and the two best practice algorithms, RMA and IPD -
but substantial between PBF and the suboptimal VC algorithm.
The reverse pattern occurred for reliability, however:
it showed a substantial difference in effect between PBF and the two best practice algorithms only.

@@

Figure \@ref(fig:figk) indicates that PBF showed increasing specificity at higher levels of $k$,
while sensitivity was relatively unaffected.
RMA and IPD showed a similar pattern,
although their specificity was at a ceiling.
Only VC showed decreasing sensitivity with an increasing number of groups;
this is because the probability of obtaining false negatives increases with the number of groups [as also noted by @hedgesVotecountingMethodsResearch1980].
This difference in pattern of effects explains why number of samples had a moderate effect on the difference between algorithms (see Table \@ref(tab:tabeffect)).

@@

<!-- In the first use case of `pbf()`, an `lm()` is ran for each sample. All `lm` objects are stored in a list which is passed to `pbf()`. -->
<!-- `pbf()` supports lists of all objects that `bain()` also supports. All supported types are specified in bain vignette *REF*. One exception is the use of named vectors, which will be covered later. -->
<!-- ```{r} -->
<!-- lm_sample1 <- lm(postnumb~site-1, sample1) -->
<!-- lm_sample2 <- lm(postnumb~site-1, sample2) -->
<!-- lm_sample3 <- lm(postnumb~site-1, sample3) -->

@@

<!-- In the first use case of `pbf()`, an `lm()` is ran for each country.  -->
<!-- All `lm` objects are stored in a list which is passed to `pbf()`. -->
<!-- `pbf()` supports lists of all objects that `bain()` also supports.  -->
<!-- All supported types are specified in the `bain` vignette.  -->
<!-- One exception is the use of named vectors, which will be covered later. -->
<!-- ```{r} -->
<!-- fit_US <- lm(soc ~ grp + her, data = USa) -->
<!-- fit_DK <- lm(soc ~ grp + her, data = DKa) -->
<!-- fit_NL <- lm(soc ~ grp + her, data = NLa) -->

@@

A third use case occurs when the raw data from different samples are not available.
This may happen, for example, when aggregating findings from the published literature (similar to meta-analysis).
In this case, one can use the default interface of `bain`, as explained in [@hoijtink2019tutorial].
This function requires four arguments: A named vector of parameter estimates, their asymptotic covariance matrix, the original sample size, and the number of within-group and between-group parameters.
Note that, when analyzing a single parameter per sample, the standard error is sufficient to construct the asymptotic covariance matrix.
Thus, this method can be applied to data that have been prepared for classic meta-analysis (effect sizes and their sampling variances).
Importantly, unlike meta-analysis, the present method is suitable for conceptual replications.
It does not require uniform effect size measures across studies.
The example below illustrates how to aggregate evidence for one hypotheses across three studies that each used different methods.
<!-- CJ: What I'd like to do here is show how to aggregate a t-test, a regression coefficient and a correlation coefficient -->

@@

The results suggest substantial evidence for the hypothesis that there is a positive association between family morality and political conservatism.
Although each study used a different method to assess this hypothesis,
their evidence can be synthesized using `pbf()`.

@@

<!-- It is interesting that these estimates are not identical to the other examples... Is that because we do not have ALL information available in this use case, or is something off in the script? -->
<!-- CJ: We should ask Herbert about this, but this example won't make it into this paper. If you want, you can send Herbert a reproducible example of the 'problem'!-->

@@

In conclusion, this study evaluated the performance of the product Bayes factor as a method for evidence synthesis,
and compared it against other commonly used evidence synthesis methods under different simulation conditions.
Compared to the other methods,
PBF had the highest overall accuracy.
This was primarily due to its greater sensitivity.
However, PBF had lower specificity than all other algorithms, suggesting a trade-off between sensitivity and specificity.
The other algorithms showed ceiling effects in specificity, limiting their sensitivity.
The performance of the PBF was most strongly affected by sample size,
followed by the number of samples and reliability.
We introduced a user-friendly implementation of the PBF in the `bain` R-package,
and demonstrated its use with various analysis techniques in R,
as well as with sufficient statistics that are already routinely coded for meta-analysis (i.e., effect sizes and their sampling variance).
This means that researchers can now use the PBF to aggregate evidence in situations where classic meta-analytic methods are less suitable.
For example, when one informative hypothesis has been evaluated in several replication studies,
but these replication studies are quite heterogeneous because they sample from different populations and use different methods or analysis techniques.
Especially when the number of replication studies is too small to adequately account for these sources of between-study heterogeneity,
the PBF may be a useful method to aggregate evidence for the common informative hypothesis.
Researchers should be aware that the PBF trades off increased sensitivity for decreased specificity,
and that it addresses a different research question than other research synthesis methods.
This highlights the importance of careful interpretation of the results,
and consideration of the research question when selecting an aggregation method.
In sum,
our results suggest that PBF is a useful evidence synthesis method,
which is now broadly accessible due to its inclusion in the `bain` R-package.

\newpage
# Highlights

* Many research synthesis methods make strong assumptions about between-studies heterogeneity that are violated when studies are conceptually replicated.
* The product Bayes factor (PBF) aggregates evidence for an informative hypothesis across conceptual replication studies without imposing assumptions about heterogeneity.
* This paper introduces a user-friendly way to compute the PBF for a variety of widely used models via the `pbf()` function in the `bain` R-package.
* A simulation study shows favorable performance for PBF relative to random effects meta-analysis, individual participant data meta-analysis, and vote counting.
* Three tutorial examples illustrate distinct use cases of the method.

# Data Availability Statement

All analysis code is available in a version-controlled repository at <https://github.com/cjvanlissa/bayesynth>.
